### 2023-12-02 main.tex
ll
kk

that acts diagonally as $C|{n}\rangle=\twoj(\twoj+N)|{n}\rangle$ and belogs to the center of ${gl}(N)$ (i.e. it commutes with all the algebra elements).  

@@

    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}

@@

\begin{align*}
R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{\xi_{1}^{x}!\ldots r_{N}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots, \xi_{N}^{x}|
	\\&
	\sum_{s^{x}\in \Omega_{x},}s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|
	\\&
	\sum_{n^{x}\in\Omega_{x}}\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|
 \\=&\sum_{r^{x}\in \Omega_{x}}
	\xi_{a}^{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots,\xi_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,\xi_{N}^{x}|
	\\=&
	\left(E_{ba}^{x}\right)^{T}
\end{align*}
where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
\end{comment}
\paragraph{Elements of the duality matrix.}
Consider the matrix $D$ defined in \eqref{dualityMatrix}.
We aim to show that its matrix elements coincide with duality function \eqref{dualityElements}, i.e.
\begin{equation}\label{proofDualityElements}
\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}\,.
\end{equation}
Fix an arbitrary site $x\in V$, then we have that 
\begin{align}
	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber
	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
\end{align}
\todo{something wrong...}
where we used \eqref{transpositionPropertyR}. \\
On one hand, on the extra-site $u(x)$ we have 
\begin{align}
\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
\end{align}
where  we used the orthogonality relation \eqref{ortho}. 
On the other hand, on the site $x$, we have 
\begin{align}
&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\cdots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)\nonumber
\\&
\hspace{2.cm}\qquad\times |\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
%\\&=
%\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
%\\&
%\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\\&=
\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\cdots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\cdots(n_{N-1}^{x}-k_{N-1})!}\nonumber
\\& 
\hspace{2.cm}\qquad\times \frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\cdots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
\\&=
\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
\end{align}
where we used the definitions of the action of $E_{ab}$  and the orthogonality relations \eqref{ortho}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
\begin{flushright}
    $\square$
\end{flushright}

>>>>

that acts diagonally as $C|{n}\rangle=\twoj(\twoj+N)|{n}\rangle$ on any state $|n\rangle$ and belogs to the center of ${gl}(N)$ (i.e. it commutes with all the algebra elements).  

@@

    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)} )_{x\in V}
\todo{OK? but this has no index $x$?}

@@

R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{\xi_{1}^{x}!\ldots r_{N}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots, \xi_{N}^{x}|
	\sum_{s^{x}\in \Omega_{x},}s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|
	\sum_{n^{x}\in\Omega_{x}}\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|
 \\=&\sum_{r^{x}\in \Omega_{x}}
	\xi_{a}^{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots,\xi_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,\xi_{N}^{x}|
	\left(E_{ba}^{x}\right)^{T}
where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
\paragraph{Elements of the duality matrix.}
Consider the matrix $D$ defined in \eqref{dualityMatrix}.
We aim to show that its matrix elements coincide with duality function \eqref{dualityElements}, i.e.
\begin{equation}\label{proofDualityElements}
\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}\,.
Fix an arbitrary site $x\in V$, then we have that 
	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\right)\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber
	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
\todo{something wrong...}
where we used \eqref{transpositionPropertyR}. \\
On one hand, on the extra-site $u(x)$ we have 
\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\right)\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
\todo{what happens to $q_N$?}
where  we used the orthogonality relation \eqref{ortho}. 
On the other hand, on the site $x$, we have 
&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\cdots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)\nonumber
\hspace{2.cm}\qquad\times |\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
%\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
%\\&
%\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\cdots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\cdots(n_{N-1}^{x}-k_{N-1})!}\nonumber
\hspace{2.cm}\qquad\times \frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\cdots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
where we used the definitions of the action of $E_{ab}$  and the orthogonality relations \eqref{ortho}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
